Deeply Virtual Compton Scattering measurement off bound protons

### 2018-08-10 eg6-letters/incoherent/adhocreview/1st_adhoc_comments.tex
implementing some of the suggestions
implement all the minor corrections

\title{First round comments from the Ad-hoc rewiew committee \\
 (Maurik Holtrop , Kevin Giovankl, and Zein-Eddine Meziani)}

@@

\item    In the title, add an "a":  "Deeply Virtual Compton Scattering off a bound proton", or make proton plural (protons).\\
   \textcolor{blue}{ }

\item    First sentence of abstract, does "measurement of incoherent deeply 
   virtual..." work better?\\
   \textcolor{blue}{ }

\item    Third sentence, replace "have been compared" with the more active "are compared"\\
   \textcolor{blue}{ }

\item    Line27: leave out "the fact"\\
   \textcolor{blue}{ }

\item    Rephrase line 34. Perhaps:  "correlations can be revealed"\\
   \textcolor{blue}{ }

\item    Line 46 - 49: Perhaps make it more clear that in the coherent case the scattering is off the entire nucleus, and that for the incoherent case the nucleon is ejected? Is that a correct interpretation of what is going on?\\
   \textcolor{blue}{ }

\item    Line 78: "amplitude that contains", or make amplitude plural.\\
   \textcolor{blue}{ }

\item    Line 154, you do not define what was used for $t_min$, and how it was 
   determined.\\
   \textcolor{blue}{ }

\item    Line 206: To make it more clear to the reader what you are doing with 
   the data, you should explicitly state that you make a fit of the $\phi$ 
      distributions, and then extract the $a_0$ value as $A_{LU}$(90). You 
      should also explicitly state that when plotting versus one kinematic 
      variable, you integrate over all the other kinematic variables. This 
      relates to comment \#2 above.\\
   \textcolor{blue}{ }

\item    Line 207: "Fig 4 presents ..." and line 215: "We present in Fig 5". 
   One is passive, the other active. It is probably better to choose one or the 
      other, but not mix them.\\
   \textcolor{blue}{ }

\item    Line 221: Either "Their model uses a nuclear spectral function" or 
   "Their model uses nuclear spectral functions".\\
   \textcolor{blue}{ }

\item    Line 238: -> "on a free proton target".\\
   \textcolor{blue}{ }

\item    Line 241: "ratios show 20\%-40\% lower asymmetries" (drop "a")\\
   \textcolor{blue}{ }

\item    Line 243: rewrite to not have "effect" twice in the sentence so close together.\\
   \textcolor{blue}{ }

\item    Line 260: Rewrite your last sentence. Suggestion: "This surprising 
   result opens a new avenue for progress in understanding quarks and gluons in 
      the nuclear medium."\\
   \textcolor{blue}{ }

>>>>

\title{First round comments from the Ad-hoc rewiew committee \\
 (Maurik Holtrop, Kevin Giovankl, Zein-Eddine Meziani)}

@@

\item    In the title, add an "a":  "Deeply Virtual Compton Scattering off a bound proton", or make proton plural (protons).\\
   \textcolor{blue}{Updated. "protons"}

\item    First sentence of abstract, does "measurement of incoherent deeply 
   virtual..." work better?\\
   \textcolor{blue}{Updated. }

\item    Third sentence, replace "have been compared" with the more active "are compared"\\
   \textcolor{blue}{Replaced. }

\item    Line27: leave out "the fact"\\
   \textcolor{blue}{Cleaned. }

\item    Rephrase line 34. Perhaps:  "correlations can be revealed"\\
   \textcolor{blue}{Cleaned. }

\item    Line 46 - 49: Perhaps make it more clear that in the coherent case the scattering is off the entire nucleus, and that for the incoherent case the nucleon is ejected? Is that a correct interpretation of what is going on?\\
   \textcolor{blue}{Updated.}

\item    Line 78: "amplitude that contains", or make amplitude plural.\\
   \textcolor{blue}{Cleaned.}

\item    Line 154, you do not define what was used for $t_{min}$, and how it 
   was determined.\\
   \textcolor{blue}{The definitions is added.}

\item    Line 206: To make it more clear to the reader what you are doing with 
   the data, you should explicitly state that you make a fit of the $\phi$ 
      distributions, and then extract the $a_0$ value as $A_{LU}$(90). You 
      should also explicitly state that when plotting versus one kinematic 
      variable, you integrate over all the other kinematic variables. This 
      relates to comment \#2 above.\\
      \textcolor{red}{Cleaned. ( I am not sure this is needed as it is 
      mentioned at the beginning of the paragraph).}

\item    Line 207: "Fig 4 presents ..." and line 215: "We present in Fig 5". 
   One is passive, the other active. It is probably better to choose one or the 
      other, but not mix them.\\
   \textcolor{blue}{Cleaned.}

\item    Line 221: Either "Their model uses a nuclear spectral function" or 
   "Their model uses nuclear spectral functions".\\
   \textcolor{blue}{Cleaned.}

\item    Line 238: -> "on a free proton target".\\
   \textcolor{blue}{Corrected. }

\item    Line 241: "ratios show 20\%-40\% lower asymmetries" (drop "a")\\
   \textcolor{blue}{Corrected.}

\item    Line 243: rewrite to not have "effect" twice in the sentence so close together.\\
   \textcolor{blue}{Cleaned.}

\item    Line 260: Rewrite your last sentence. Suggestion: "This surprising 
   result opens a new avenue for progress in understanding quarks and gluons in 
      the nuclear medium."\\
   \textcolor{blue}{Added.}

### 2018-08-10 eg6-letters/incoherent/incoherent_prl.tex
implement all the minor corrections

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=(q+p)^2$) greater than 2 GeV to avoid the nucleon resonance region.  
The $t$, transferred momentum squared to the recoil proton assuming an 
on-shell proton at rest, was required to be greater than a minimum allowed 
value at given Q$^2$ and W ($t~>~t_{min}$).  Then, the exclusivity of the 
incoherent DVCS events was ensured by imposing constraints on the kinematical 
variables resulting from conserving the four-momentum in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables are shown in FIG.~\ref{fig:kin-cuts}. We also rejected events where a 
$\pi^0$ was identified by the invariant mass of two photons. At the end of
this selection process, about 30k events 
passed all the requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

@@

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
$x_{B}$ or $t$) and nine bins in the azimuthal angle ($\phi$).  
FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$, $x_{B}$, and $t$. The curves on the plots are fits 
of the form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$. The main contributions 
to systematic uncertainties on these fits are from the choice of the DVCS 
exclusivity cuts (6\%) and the large bin size (7\%). The systematic uncertainties
sum up to less than 10\% for all data points and thus always remain significantly 
smaller than the statistical errors.

@@

We present in FIG.~\ref{fig:alu90} the dependence of the fitted $A_{LU}$ 
values at $\phi$~=~90$^{\circ}$ on the kinematical variables $Q^2$, $x_{B}$, 
and $t$. Within the given uncertainties, $A_{LU}$ does not indicate a strong 
dependence on $Q^2$. The $x_{B}$ and $t$ dependencies are compared to 
theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. Their model uses nuclear spectral function and 
considers mainly off-shell effects. The calculations are carried out at slightly 
different kinematics than our data but still provide important guidance. The 
experimental results appear to have smaller asymmetries especially at low 
$x_{B}$ than the calculations. These differences may arise from nuclear 
effects which are not taken into account in the model, such as long-range 
interactions. On the graph for $-t$ dependence, we show previous measurements 
by the HERMES collaboration \cite{Airapetian:2009cga}, in which only electrons
and photons were measured. Due to the large experimental uncertainties of the HERMES 
points, the two measurements are completely compatible.

@@

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD framework. 
To explore this idea, we construct 
the ratio of $A_{LU}$ for bound protons to that on free proton target.  
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the 
BSA ratio based on interpolation of the free proton asymmetries from  
CLAS \cite{Girod:2007aa} as a function of the kinematical variable
$x_B$. The $A_{LU}$ ratios show a 20\%-40\% lower asymmetries for a bound proton compared 
to the free proton mirroring a form of EMC effect but with a surprising 
large effect, in particular at low $x_B$. The measurements disagree with the off-shell \cite{simonetta_2} 
and the on-shell calculations that use the medium modified GPDs as calculated from 
the quark-meson coupling model \cite{Guzey:2008fe}. In particular, the difference becomes
large at lower $x_B$, 
where the off-shell model predicts an enhancement of the ratio, where our experiment 
shows a sharp drop. This measurement shows that an important nuclear effect is
missing from the existing models in order to explain this strong quenching of
the BSA.

@@

%conclusion
In summary, we have presented our BSA measurements 
associated with incoherent DVCS off $^4$He using an upgraded setup of the CLAS 
spectrometer at Jefferson Lab. Our results were compared to model 
calculations based on different assumptions of the nuclear medium effects at 
the partonic level. The bound-proton BSA is largely suppressed compared to 
the free proton BSA. This surprising result opens a new avenue 
for progress in the understanding of the quarks and gluons behavior in the
nuclear medium.

>>>>

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=(q+p)^2$) greater than 2 GeV to avoid the nucleon resonance region. 
The $t$, transferred momentum squared to the recoil proton assuming an on-shell 
proton at rest, was required to be greater than a minimum allowed value at 
given Q$^2$ and W ($t>~t_{min}(=~- Q^{2}~\frac{2(1- x_{B})(1~-~\sqrt{1 
+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). Then, the exclusivity of the incoherent DVCS events was ensured 
by imposing constraints on the kinematical variables resulting from conserving 
the four-momentum in the reaction $ep\rightarrow e'p'\gamma$.  These 
kinematical variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
We also rejected events where a $\pi^0$ was identified by the invariant mass of 
two photons. At the end of
this selection process, about 30k events 
passed all the requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

@@

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
$x_{B}$, or $t$) and then nine bins in the azimuthal angle ($\phi$).   
FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$ (integarted over full $x_{B}$ and $t$ ranges), 
$x_{B}$ (integarted over full $Q^{2}$ and $t$ ranges), and $t$ (integarted over 
full $Q^{2}$ and $x_{B}$ ranges). The curves on the plots are fits of the form 
$\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$.  The main contributions to 
systematic uncertainties on these fits are from the choice of the DVCS 
exclusivity cuts (6\%) and the large bin size (7\%). The systematic 
uncertainties sum up to less than 10\% for all data points and thus always 
remain significantly smaller than the statistical errors.

@@

FIG.~\ref{fig:alu90} presents the dependence of the fitted $A_{LU}$ values at 
$\phi$~=~90$^{\circ}$ ($a_{0}$ parameter from the individual fits in 
FIG.~\ref{fig:alu}) on the kinematical variables $Q^2$, $x_{B}$, and $t$.  
Within the given uncertainties, $A_{LU}$ does not indicate a strong dependence 
on $Q^2$.  The $x_{B}$ and $t$ dependencies are compared to theoretical 
calculations performed by S.~Liuti and K.~Taneja \cite{simonetta_2}. Their 
model uses a nuclear spectral function and considers mainly off-shell effects.  
The calculations are carried out at slightly different kinematics than our data 
but still provide important guidance. The experimental results appear to have 
smaller asymmetries especially at low $x_{B}$ than the calculations. These 
differences may arise from nuclear effects which are not taken into account in 
the model, such as long-range interactions.  On the graph for $-t$ dependence, 
we show previous measurements by the HERMES collaboration 
\cite{Airapetian:2009cga}, in which only electrons
and photons were measured. Due to the large experimental uncertainties of the HERMES 
points, the two measurements are completely compatible.

@@

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD 
framework.  To explore this idea, we construct the ratio of $A_{LU}$ for bound 
protons to that on a free proton target. 
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
interpolation of the free proton asymmetries from  CLAS \cite{Girod:2007aa} as 
a function of the kinematical variable $x_B$. The $A_{LU}$ ratios show 
20\%-40\% lower asymmetries for a bound proton compared to the free proton 
mirroring a form of EMC effect but with a surprising large modification, in 
particular at low $x_B$. The measurements disagree with the off-shell 
\cite{simonetta_2} and the on-shell calculations that use the medium modified 
GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}. In 
particular, the difference becomes large at lower $x_B$, where the off-shell 
model predicts an enhancement of the ratio, where our experiment shows a sharp 
drop. This measurement shows that an important nuclear effect is missing from 
the existing models in order to explain this strong quenching of the BSA.

@@

%conclusion
In summary, we have presented our BSA measurements 
associated with incoherent DVCS off $^4$He using an upgraded setup of the CLAS 
spectrometer at Jefferson Lab. Our results were compared to model 
calculations based on different assumptions of the nuclear medium effects at 
the partonic level. The bound-proton BSA is largely suppressed compared to 
the free proton BSA. This surprising result opens a new avenue for progress in 
the understanding quarks and gluons in the nuclear medium.
